DNSKEY Management

### 2012-12-07 paper/paper.tex
new figure for DNSSEC removal

For DNSSEC's shutdown to be clean and complete, the parent zone and any TAR must be cleaned from whatever DS record they contain for the zone which is being withdrawn from DNSSEC.

>>>>

\begin{figure}
  \includegraphics[width=\linewidth]{trust-chain-tar-no-key}
  \caption{Illustration of a domain having disabled DNSSEC with a TAR still serving a record for it.}
  \label{fig:remaining-tar}
\end{figure}

For DNSSEC's shutdown to be clean and complete, the parent zone and any TAR (figure~\ref{fig:remaining-tar}) must be cleaned from whatever DS record they contain for the zone which is being withdrawn from DNSSEC.
